### 2015-05-14 evaluation.tex
space hack

\noindent\textbf{Race-Checking }
%
Table~\ref{tab:stats} presents statistics for all our benchmarks: lines of code (LoC); number of entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of racy pairs reported by \whoop (\#Racy Pairs); number of racy memory regions identified by \whoop (\#Racy MRs); and number of races discovered by \corral using a context-switch bound (csb) of 2 (\#Races Found). Using a higher csb did not uncover any further races; this might mean that races in our benchmarks require only one or two context-switches to manifest, or that \corral hit its bounds before discovering a deeper bug. \corral did not discover any races that \whoop did not already report.  This is expected, as \whoop aims for soundness, and increases our confidence in the implementation of \whoop.

>>>>

\noindent\textbf{Race-Checking }
%
Table~\ref{tab:stats} presents statistics for all our benchmarks: lines of code (LoC); number of entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of racy pairs (\#Racy Pairs) and number of racy memory regions (\#Racy MRs) reported by \whoop; and number of races discovered by \corral using a context-switch bound (csb) of 2 (\#Races Found). Using a higher csb did not uncover any further races; this might mean that races in our benchmarks require only one or two context-switches to manifest, or that \corral hit its bounds before discovering a deeper bug. \corral did not discover any races that \whoop did not already report.  This is expected, as \whoop aims for soundness, and increases our confidence in the implementation of \whoop.
